A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-12 sanity/paper1.tex
Link to homepage
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1078 43ef1190-90fd-4dd7-a769-d0121f02b80e

In this paper, we study to what extent SPARQL endpoints, vocabulary
and data publishers support these standards.\todo{link to dump}

>>>>

In this paper, we study to what extent SPARQL endpoints, vocabulary
and data publishers support these standards. Data and code to
reproduce this work will be available at
\url{http://folk.uio.no/kjekje/#cache-survey}.
